Assessing the Global COVID19 Impact on Air Transport with Open Data

### 2021-06-21 paper.Rmd
please loop

```{r}
#If someone needs filters below, here we can control any selective sample
#Filtering Brazilian and European data to reduce the sample (and csv) size
#Currently, those filters are not in use in the code, they are here just in case.

bra_10_apts <- c("SBBR", "SBGR", "SBSP", "SBKP", "SBRJ", "SBGL", "SBCF", "SBSV", "SBPA", "SBCT")
eur_apts <- c("EHAM","LFPG","EGLL","EDDF","EDDM","LEMD","LIRF","LEBL","EGKK","LSZH")
study_airports <- c(bra_10_apts, eur_apts)
```

@@

1.2.1 Gather and prepare data
```{r}
#Reading raw data

@@

```{r}
#Joining countries and regions
# NOTE: the airports.csv file below is the downloaded file from www.ourairports.org.

airports <- read_csv("data-raw/airports.csv") %>% mutate(continent = case_when(is.na(continent) ~ "NA", TRUE ~ continent))
apt_countries <- airports %>% transmute(ICAO = ident, CTRY = iso_country)

#There are missing airports
apt_countries <- apt_countries %>% add_row(ICAO  = c("SPJC", "YBMC", "LSZM", "YSCH", "EPLB", "K3M3", "VV01", "SC28", "CWF2", "EHDB", "74XA", "HE13"), CTRY  = c("PE", "AU", "FR", "AU", "PL", "US", "VN", "US", "CA", "NL", "US", "EG"))

#If you need to write
#write_csv(apt_countries, "./data/apt_countries.csv")

#Joining to ADEP
fb2 <- left_join(fb1, apt_countries, by = c("ADEP" = "ICAO")) %>% mutate(ADEP_CTRY = CTRY, .keep = "unused", .after = ADEP)
#Joining to ADES
fb3 <- left_join(fb2, apt_countries, by = c("ADES" = "ICAO")) %>% mutate(ADES_CTRY = CTRY, .keep = "unused", .after = ADES)

@@

# Associate the regions
a <- airports %>% filter(continent == "EU") %>% select(iso_country) %>% unique()
eur_countries <- a$iso_country

>>>>

```{r}
###Preparatory codes

#If someone needs filters below, here we can control any selective sample
#Filtering Brazilian and European data to reduce the sample (and csv) size
#Currently, those filters are not in use in the code, they are here just in case.
bra_10_apts <- c("SBBR", "SBGR", "SBSP", "SBKP", "SBRJ", "SBGL", "SBCF", "SBSV", "SBPA", "SBCT")
eur_apts <- c("EHAM","LFPG","EGLL","EDDF","EDDM","LEMD","LIRF","LEBL","EGKK","LSZH")
study_airports <- c(bra_10_apts, eur_apts)

###Preparing airport file
#NOTE: the airports.csv file below is the downloaded file from www.ourairports.org.
airports <- read_csv("data-raw/airports.csv") %>% mutate(continent = case_when(is.na(continent) ~ "NA", TRUE ~ continent))

#There are missing airports and too much variables
apt_countries <- airports %>% transmute(ICAO = ident, CTRY = iso_country) %>% add_row(ICAO  = c("SPJC", "YBMC", "LSZM", "YSCH", "EPLB", "K3M3", "VV01", "SC28", "CWF2", "EHDB", "74XA", "HE13"), CTRY  = c("PE", "AU", "FR", "AU", "PL", "US", "VN", "US", "CA", "NL", "US", "EG"))

#If you need to write
#write_csv(apt_countries, "./data/apt_countries.csv")
#apt_countries is ready.

# Associate the regions
a <- airports %>% filter(continent == "EU") %>% select(iso_country) %>% unique()
eur_countries <- a$iso_country
#eur_countries is ready.

@@

1.2.1 Gather and prepare data

```{r}
#Reading raw data

@@

```{r}
#Joining to ADEP
fb2 <- left_join(fb1, apt_countries, by = c("ADEP" = "ICAO")) %>% mutate(ADEP_CTRY = CTRY, .keep = "unused", .after = ADEP)
#Joining to ADES
fb3 <- left_join(fb2, apt_countries, by = c("ADES" = "ICAO")) %>% mutate(ADES_CTRY = CTRY, .keep = "unused", .after = ADES)

@@
